A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-06 paper/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster using kinematic information from Gaia, stellar rotation
  periods from TESS, and Li abundances from ground-based spectra.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short-cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using the Gaia data; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems likely to be an effective path toward expanding the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of known transiting
    exoplanets}.  Planets older than $10^9$ years are shown with gray
    markers.  Planets younger than a gigayear with ${\rm
    Age}/\sigma_{\rm Age} > 3$
    are shown in color.  \pn\ is shown with a star.  The large radii
    of the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (July
    2, 2021).
		\label{fig:rp_period_age}
	}
\end{figure}

@@

In the context of the known transiting planets, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precisely measured ages below 100\,Myr include K2-33b, DS~Tuc~Ab,
HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
\pn\ is currently the smallest of these systems ($\approx
3.3\,R_\oplus$), which may hint at selection effects in the young
planet sample \citep{zhou_2021_tois}.  Assuming that these planets
have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$, their
large sizes and presumed low densities are in accord with the
expectation that mini-Neptunes start their lives with large primordial
atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit differs from observed misalignments in
number of other close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Unlike these older planets, the properties of \pn\ seem to be
consistent with a quiescent disk-driven migration history.  The
alternative scenario of in-situ formation is disfavored on theoretical
grounds: the required disk mass would likely drive migration, and so
lacks internal consistency
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.

Ultimately though, the main advance of this work was a precise measurement of
the age of \pn.   The age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.  Table~\ref{tab:v05}
enables similar crossmatches to
already known planets, as well as forthcoming planets from the TESS
mission \citep{ricker_transiting_2015,guerrero_tess_2021}.  An
alternative path toward age-dating more planets could be to identify kinematic associations
around known exoplanet host stars using positions and tangential velocities
from Gaia, and to then verify these associations with ancilliary
rotation periods and spectroscopy \citep[{\it e.g.},][]{tofflemire_tess_2021}.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f15supp.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Binarity indicators for rotators in \cn.} 
    Data are as in the lower panel of
    Figure~\ref{fig:age}.  Astrometric binaries ($\mathrm{RUWE}>1.2$)
    appear in red; photometric binaries ($>$0.3\,mag above an
    empirical isochrone; 20\% of stars) are orange.  
    Over $0.6<\bpmrpo<1.5$, the detected rotation periods in binaries tend to 
    fall below the slow sequence.
    %FIXME!
		% Over $0.5<\bpmrpo<1.3$, Set $\mathcal{B}$ has \replaced{281}{523} stars.
		% Dividing these stars into ``slow'' and ``fast'' sequences by eye,
		% the fraction of stars showing signs of binarity in the slow and fast
		% subsamples are \replaced{30\% (63/210)}{27\% (106/289)} and
		% \replaced{56\% (40/71)}{51\% (68/134)}, respectively.
		\label{fig:binarity}
	}
\end{figure*}

@@

\subsection{Long Cadence Data}
\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Transit model residuals through time}.  
    {\it Left:}
		Phase-folded transit of Kepler 1627b, with stellar
    variability removed, binned by Kepler quarter.
    Black points are binned to 20 minute intervals.
    The 1-$\sigma$ model uncertainties and the maximum {\it a
    posteriori} model are shown as the faint purple band, and the dark
    purple line.
    {\it Right:}
    As on the left, with the transit removed.
    Quarters 6 and 7 show a consistent deviation in the second half of
    the transit.
		\label{fig:phasequarter}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit model residuals through time (Part 2)}.  
    {\it Left:}
		Phase-folded transit of Kepler 1627b, with stellar
    variability removed, binned by year of observation.
    Points and models are as in Figure~\ref{fig:phasequarter}.
    {\it Right:}
    As on the left, with the transit removed.
		\label{fig:phaseyear}
	}
\end{figure*}

We assumed a quadratic limb-darkening law, with the uninformative prior
advocated by CITET Kipping2013.

% In the first approach, we adopted uniform priors centered on the
% interpolated CITET Claret+2011 coefficients in the Kepler-band, with
% with $\pm 0.2$ in either parameter.  The fit was not as good.

Our default stellar variability model (RotGPtransit) allows for a
\texttt{RotTerm} GP kernel, with a logjitter term to inflate the
uncertainties to account for excess white noise.  (This results in an
inflation of the uncertainties by a factor of about three).

We considered including an additive \texttt{SHOTerm} kernel to account
for stochastic noise (RotStochGPtransit).  This didn't seem to affect
the results much, so we opted for the simpler model.

Figure~\ref{fig:phasefold} shows X, Y, Z.  The residuals during the
transit may hint at some small degree of unfitted signal -- in the
sense that the observations are systematically high in the first half
of transit, and low in the second half.  This is the phase of maximal
scatter during each orbital period (TODO: in vs out of transit
scatter).  The amplitude of the anomaly is $\approx$30\,ppm.

To explore the origin of the anomaly, we binned the Kepler data over
quarters (Figure~\ref{fig:phasequarter}) and years
(Figure~\ref{fig:phaseyear}).  In Figure~\ref{fig:phasequarter}
Quarter 6 shows the strongest asymmetry out of any of the quarters: a
deviation of about 3\,ppt from expectation.  Quarter 7 shows an
anomaly at roughly the same transit phase.  Year 2 correspondingly
shows the strongest anomaly out of any year in
Figure~\ref{fig:phaseyear}.

We considered three possible explanations for the anomaly: gravity
darkening, transit timing variations, and spot-crossing events.

Gravity darkening (e.g., CITE Masuda 2015) is based on the premise
that the rapidly rotating star becomes oblate, and brighter near the
poles than the equator.  The fractional shape change due to gravity
darkening is on the order of $(P_{\rm break}/P_{\rm rot})^2$, for
$P_{\rm break}$ the break-up rotation period, and $P_{\rm rot}$ the
rotation period.  Using the parameters from Table~\ref{tab:posterior},
this yields an expected 1.6\% distortion of the $\approx$1.8\,ppt
transit depth: {\it i.e.}, an absolute deviation of $\approx$3\,ppm.
This is smaller than the observed anomaly by an order of magnitude,
and therefore seems unlikely.

@@

The final possibility is that of starspot crossings.  Given the high
expected spot-covering fractions for young stars ({\it e.g.},
\citealt{morris_relationship_2020}, \citealt{plavchan_planet_2020}),
\pn\ may cross spot groups on the stellar surface in projection.
Spot-crossing anomalies often reach amplitudes exceeding 100\,ppm
({\it e.g.}, CITE Dai 2018, maybe Southworth's recent stuff).  For our
system,  $P_{\rm orb}/P_{\rm rot} \approx 2.76$.  This means that
every 4 transits (and 11 stellar rotations), the planet crosses over
roughly the same stellar longitude.  Over a given quarter, this could
occur at most three times, assuming the spot groups are persistent.

This could provide a plausible path to creating the distorted transit
signal, based on the amplitudes involved.  However, the typical S/N
per Kepler transit is $\approx8$, making individual spot-crossing
unresolved, and this scenario challenging to test.  {\it A priori},
one would also expect the spot-crossing events to not have a preferred
orbital phase, so that they would average out over the $\approx200$
Kepler transits.  Nonetheless, given the available data, it is our
best explanation for what we believe is real additional photometric
scatter observed during the transits.

\subsection{Short Cadence Data}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f12.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded short cadence transit of Kepler\,1627 Ab}.  
    The precision with which the impact parameter can be measured is
    higher than from the long cadence data.
		\label{fig:phase_slc}
	}
\end{figure*}

Figure~\ref{fig:phase_slc} shows the result from analyzing 100 days of
short cadence (1-minute) data acquired during Quarter 15.
%TODO: get quantitative on better impact parameter...

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.6\textwidth]{Kepler1627_20210624_562_832_final.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Keck NIRC2 AO image of Kepler 1627A and Kepler 1627B.}  
    {\bf SCALEBAR DENOTES...}
    {\bf North is up, East is left}.
    \label{fig:ao}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.6\textwidth]{f6.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Gaia EDR3 renormalized unit weight error (RUWE) point
    estimates for Kepler\,1627A and other members of the $\delta$\,Lyr
    cluster.}  Since other members of the cluster with similar colors
    have comparable degrees of photometric variability, the high RUWE
    suggests that Kepler\,1627A is an astrometric binary. 
		\label{fig:ruwe}
	}
\end{figure*}

We first noted the presence of a stellar neighbor in archival
Keck/NIRC2 Kp-band adaptive optics imaging (2.12\,$\mu $m), from the
Spring semesters of both 2015 and 2019.  We acquired additional
Gemini-North/`Alopeke speckle imaging on 24 June 2021, which showed
the same companion in the 0.83\,$\mu$m notch filter, but not the
$0.56\,\mu$m filter.  Figure~\ref{fig:ao} summarizes the results of
the high-resolution imaging.  Although the companion is unresolved in
the Gaia source catalog, its existence was also suggested by the
primary star's large RUWE, relative to other members of the \cn.  The
images yield a projected separation $\rho \approx 0\farcs16$, with
$\Delta m_{832} \approx 3.1$ and $\Delta m_{\rm Kp} = 2.5$.  Using the
measured Gaia EDR3 parallax for the system, this implies a projected
separation of $53 \pm 7$.  Given the low geometric probably of a star
imaged within $\rho \approx 0\farcs16$ to be a chance companion along
the line of sight, and the large observed RUWE, we proceed under the
assumption that the companion is bound, and that the Kepler\,1627
system is binary.  Based on the
tabulation\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt},
version \texttt{2021/03/02}.} by \citet{pecaut_mamajek_2013}, the
measured magnitude differences for a G8V primary correspond to a
spectral type for the companion of $\approx$M2V ($M_\star \approx
0.44\,M_\odot$).  However, the companion should have a longer
pre-main-sequence contraction phase than the primary, which would
imply that this mass is overestimated by $\sim10$ to $20\%$.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Flares in Kepler\,1627}.  
    {\it Top:}
    The full short-cadence Kepler dataset, acquired at 1-minute
    sampling (black points) is shown with a stellar variability model
    (blue line).
    {\it Middle:}
    Residual after subtracting the stellar variability model.  Flares
    appear as spikes.
    {\it Bottom:}
    Zooms of the brightest, and third-brightest flares.  A timing
    coincidence -- that both flares have ``successors'' approximately
    one orbital period after the initial event -- is emphasized.
		\label{fig:flarezoom}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1.0\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded flares in Kepler\,1627}.  
    {\it Top:}
    As in the middle of Figure~\ref{fig:flarezoom}, phase-folded at
    the planet's ephemeris.
    {\it Bottom:}
    Fitted flare amplitudes and orbital phases -- each point
    represents one flare.
    Colors indicate relative time, from the beginning of the
    98-day short-cadence Quarter 15 dataset (dark blue) to the end (light
    yellow).
    Lower amplitude flares likely exist in the data, and were not
    examined.
		\label{fig:flarephase}
	}
\end{figure*}

@@

The short cadence (1-minute) Kepler observations span 97.7 days.
The light curve shows a significant number of flares
(Figure~\ref{fig:flarezoom}).
To quantify clean the light curve and identify the flares, we
performed the following procedure.
For cleaning, we performed the following iterative detrending procedure.
\begin{itemize}
  \item Step 1: Build a two-term mixed SHOTerm GP model with
    quasi-periodic kernels at Prot and 0.5$\times$Prot. Fit the model
    to the time, flux, and flux uncertainty.
  \item Step 2: Select points more than twice the median absolute
    deviation from the residual, and exclude them from the light
    curve.  Repeat Step 1.
  \item Step 3: On the residual from Step 2, identify all flares,
    requiring them to be at least 20 cadences apart, at least 7 median
    absolute deviations above the median baseline, and lasting at least
    2 cadences in duration.  Build the mask spanning these times, from
    5 minutes before each flare begins to 2.5 minutes after the final
    flare cadence.  Repeat Step 1 a final time.
\end{itemize}
The flares were then identified and fitted using ALTAIPONY (CITE CITE).
The fitted model is that of CITE XXX, which parametrizes the flare
with a start time, a lag time, and an amplitude (CHECK).
Figure~\ref{fig:flarephase} shows the resulting flares, amplitudes,
and phases.

There were $N_{\rm f}=24$ flares exceeding $0.5\%$ in relative flux during the
short-cadence observations.  These 24 flares spanned a total of 6.5
hours ($\sim$15 minutes per flare).  For better or worse, we noticed a
coincidence in the flare arrival times.  The coincidence is that
despite the low flare duty cycle, one orbital period after the
brightest flare, a second flare followed.  This and a similar event
are shown in Figure~\ref{fig:flarezoom}.  The timing error is good to
a $\approx0.2\%$ difference from the orbital period, which seems {\it
a priori} unlikely.  If we consider flares falling within 2\% of the
planet's orbital period after a previous flare, then 4 of the 24 flare
events have candidate ``successors''.

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster using kinematic information from Gaia, stellar rotation
  periods from TESS, and Li abundances from ground-based spectra.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using the Gaia data; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems likely to be an effective path toward expanding the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of known transiting
    exoplanets}.  Planets older than $10^9$ years are shown with gray
    markers.  Planets younger than a gigayear with ${\rm
    Age}/\sigma_{\rm Age} > 3$
    are emphasized.  \pn\ is shown with a star.  The large radii
    of the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (July
    2, 2021).
		\label{fig:rp_period_age}
	}
\end{figure}

@@

In the context of the known transiting planets, \pn\ is among the
youngest known (Figure~\ref{fig:rp_period_age}).  Comparable systems
with precise ages below 100\,Myr include K2-33b, DS~Tuc~Ab,
HIP~67522b, TOI~837b, AU~Mic~b, and the four-planet V1298~Tau system
\citep{Mann_K2_33b_2016,David_et_al_2017,newton_tess_2019,david_four_2019,bouma_cluster_2020,plavchan_planet_2020}.
\pn\ is currently the smallest of these systems ($\approx
3.3\,R_\oplus$), which may hint at selection effects in the young
planet sample \citep{zhou_2021_tois}.  Assuming that these planets
have masses between $\approx$5$\,M_\oplus$ and 10$\,M_\oplus$, their
large sizes and presumed low densities are in accord with the
expectation that mini-Neptunes start their lives with large primordial
atmospheres that are shed over the first gigayear
\citep{Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018}.  Our
suggestion of an aligned orbit differs from observed misalignments in
number of other close-in
mini-Neptunes~\citep{sanchis-ojeda_starspots_2011,albrecht_obliquities_2012,dalal_2019_hd3167,rubenzahl_tess-keck_2021}.
Unlike these older planets, \pn\ seems to have properties
consistent with a quiescent disk-driven migration history.  The
alternative scenario of in-situ formation is disfavored on theoretical
grounds: the required disk mass would likely drive migration, and so
lacks internal consistency
\citep{inamdar_formation_2015,ogihara_reassessment_2015}.

Ultimately, the main advance of this work was a precise measurement of
the age of \pn.   This age measurement was enabled by identifying the
connection of the star to the \cn\ using the Gaia data.  Table~\ref{tab:v05}
should enable similar crossmatches to
already known planets, as well as forthcoming planets from the TESS
mission \citep{ricker_transiting_2015,guerrero_tess_2021}.  An
alternative path toward age-dating more planets could be to identify kinematic associations
around known exoplanet host stars using positions and tangential velocities
from Gaia, and to then verify these associations with ancilliary
rotation periods and spectroscopy \citep[{\it e.g.},][]{tofflemire_tess_2021}.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f15supp.pdf}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf Binarity indicators for rotators in \cn.} 
    Data are as in the lower panel of
    Figure~\ref{fig:age}.  Astrometric binaries ($\mathrm{RUWE}>1.2$)
    appear in red; photometric binaries ($>$0.3\,mag above an
    empirical isochrone; 20\% of stars) are orange.  
    Over $0.6<\bpmrpo<1.5$, the detected rotation periods in binaries tend to 
    fall below the slow sequence.
    %FIXME!
		% Over $0.5<\bpmrpo<1.3$, Set $\mathcal{B}$ has \replaced{281}{523} stars.
		% Dividing these stars into ``slow'' and ``fast'' sequences by eye,
		% the fraction of stars showing signs of binarity in the slow and fast
		% subsamples are \replaced{30\% (63/210)}{27\% (106/289)} and
		% \replaced{56\% (40/71)}{51\% (68/134)}, respectively.
		\label{fig:binarity}
	}
\end{figure}

@@

\subsection{Long Cadence Data}
\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Transit model residuals through time (binned by Kepler quarter)}.  
    {\it Left:}
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  Black points are binned to 20
    minute intervals.  The 2-$\sigma$ model uncertainties and the
    maximum {\it a posteriori} model are shown as the faint purple
    band, and the dark purple line.
    {\it Right:}
    As on the left, with the transit removed.  Quarters 6 and 7 show a
    consistent deviation in the second half of the transit.
		\label{fig:phasequarter}
	}
\end{figure}

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f10.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit model residuals through time (binned by year of observation)}.  
    {\it Left:}
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  Points and models are as
    in Figure~\ref{fig:phasequarter}.
    {\it Right:}
    As on the left, with the transit removed.
		\label{fig:phaseyear}
	}
\end{figure}

We fitted the Kepler nce time series with a model that
simultaneously included the planetary transit and the stellar
variability.  The stellar variability was modelled with the
\texttt{RotationTerm} Gaussian Process kernel in \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  This kernel assumes that the variability
is generated by a mixture of two damped simple harmonic oscillators
with characteristic frequencies set by 1/$P_{\rm rot}$ and its first
harmonic.  We additionally incorporated a ``jitter'' term to inflate
the flux uncertainties in a manner that accounted for otherwise
unmodelled excess white noise, and let the eccentricity float.  For
the limb-darkening, we assumed a quadratic law, and sampled using the
uninformative prior suggested by \citet{exoplanet:kipping13}.

Our adopted model therefore included 10 free parameters for the
transit ($\{P,t_0,\log R_{\rm p}/R_\star,b,u_1,u_2,R_\star, \log g,
e\cos\omega, e\sin\omega \}$), 2 parameters for the light curve
normalization and uncertainty calibration ($\{\langle f \rangle,  \log
\sigma_f \}$), and 5 hyperparameters for the GP
($\{\sigma_{\mathrm{rot}}, \log P_{\mathrm{rot}}, \log Q_0, \log
\mathrm{d}Q, f \}$).  We also considered including an additive
\texttt{SHOTerm} kernel to account for stochastic noise, but found
that this did not significantly affect the results, and so opted for
the simpler GP kernel.  We fitted the models using \texttt{PyMC3}
\citep{salvatier_2016_PyMC3,exoplanet:theano}.  After initializing
each model with the parameters of the maximum {\it a posteriori}
model, we assumed a Gaussian likelihood, and sampled using
\texttt{PyMC3}'s gradient-based No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}. We used $\hat{R}$ as our convergence
diagnostic \citep{gelman_inference_1992}.

Figure~\ref{fig:lc} shows the resulting model in orange (top) and
purple (bottom).  While the fit appears reasonably good, an asymmetry
is present during the transit: the measured flux is systematically
high during the first half, and low in the second half.  We verified
that this effect is not caused by our stellar variability model by
exploring an alternative approach in which we isolated each transit
window and locally fitted out polynomial trends, and then binned all
the observed transits; the asymmetry was still present, at a
comparable amplitude.

Figures~\ref{fig:phasequarter} and~~\ref{fig:phaseyear} show the
Kepler data binned over quarters and years.  In
Figure~\ref{fig:phasequarter} Quarter 6 shows the strongest asymmetry
out of any of the quarters: a deviation of about 3\,ppt from
expectation.  Quarter 7 shows an anomaly at roughly the same transit
phase.  Year 2 correspondingly shows the strongest anomaly out of any
year in Figure~\ref{fig:phaseyear}.

We considered three possible explanations for the anomaly: gravity
darkening, transit timing variations, and spot-crossing events.
Gravity darkening is based on the premise that the rapidly rotating
star becomes oblate, and brighter near the poles than the equator
\citep[{\it e.g.},][]{masuda_spin-orbit_2015}.  The fractional shape
change due to gravity darkening is on the order of $(P_{\rm
break}/P_{\rm rot})^2$, for $P_{\rm break}$ the break-up rotation
period, and $P_{\rm rot}$ the rotation period.  Using the parameters
from Table~\ref{tab:posterior}, this yields an expected 1.6\%
distortion of the $\approx$1.8\,ppt transit depth: {\it i.e.}, an
absolute deviation of $\approx$3\,ppm.  The observed residual has an
amplitude of $\approx 30\,{\rm ppm}$.  Since the expected signal is
smaller than the observed anomaly by an order of magnitude, gravity
darkening seems to be an unlikely explanation.

@@

The final possibility is that of starspot crossings.  Young stars are
thought to have higher spot-covering fractions than old stars ({\it
e.g.}, \citealt{morris_relationship_2020},
\citealt{plavchan_planet_2020}).  Young solar-type stars may also host
dark starspots at high stellar latitudes \citep[{\it e.g.},
EK~Dra][]{strassmeier_starspots_2009}, though interferometric imaging
of spotted giant stars has found different starspot latitude distributions than
those inferred from Doppler imaging
\citep{roettenbacher_contemporaneous_2017}.  Regardless, for any
spot-crossing anomalies to add coherently over the 144 Kepler
transits, it seems likely that we would need either for spots to be
persistent at a particular latitude (and for a slightly misaligned
orbit), or for a ``stroboscopic'' longitudinal phasing \citep[{\it
e.g.},][]{dai_stellar_2018}.  For our system, $P_{\rm orb}/P_{\rm rot}
\approx 2.76$, which means that every 4 transits and 11 stellar
rotations, the planet crosses over roughly the same stellar longitude,
which could enable the necessary phasing if the spot-groups are
long-lived.  Unforunately, the typical S/N per Kepler transit is
$\approx8$, which renders individual spot-crossing events unresolved.
Therefore, although among the possible ideas starspot crossings seem
the most likely to provide the additional photometric scatter observed
during transits, our reasoning is essentially that the expected
spot-crossing anomaly amplitudes ($\approx 100\,{\rm ppm}$) could be
correct; we are not able to definitely show that this is the correct
explanation, and the issue could deserve further exploration.

%  \subsection{Short Cadence Data}
%  
%  \begin{figure*}[t]
%  	\begin{center}
%  		\leavevmode
%  		\includegraphics[width=1\textwidth]{f12.pdf}
%  	\end{center}
%  	\vspace{-0.7cm}
%  	\caption{
%  		{\bf Phase-folded short cadence transit of Kepler\,1627 Ab}.  
%      The precision with which the impact parameter can be measured is
%      higher than from the long cadence data.
%  		\label{fig:phase_slc}
%  	}
%  \end{figure*}
%  
%  Figure~\ref{fig:phase_slc} shows the result from analyzing 100 days of
%  short cadence (1-minute) data acquired during Quarter 15.
%  %TODO: get quantitative on better impact parameter...

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f17a.pdf}
			\includegraphics[width=0.37\textwidth]{f17b.jpg}
		}

		\vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.55\textwidth]{f6.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler 1627 is a binary.} {\it Top:} High-resolution imaging
    from Gemini-North/`Alopeke ({\it left}) and Keck/NIRC2 ({\it
    right}) shows an $\approx$M2V companion at $\rho \approx
    0\farcs16$, which corresponds to a projected separation of
    $53\pm7$\,AU.  {\it Bottom:} Gaia EDR3 renormalized unit weight
    error (RUWE) point estimates for Kepler\,1627A and other members
    of the $\delta$\,Lyr cluster.  Since other members of the cluster
    with similar colors have comparable degrees of photometric
    variability, the high RUWE suggests that Kepler\,1627 is an
    astrometric binary. 
    \label{fig:kep1627binary}
	}
\end{figure*}

We first noted the presence of a stellar neighbor in archival
Keck/NIRC2 Kp-band adaptive optics imaging (2.12\,$\mu $m), from the
Spring semesters of both 2015 and 2019.  We acquired additional
Gemini-North/`Alopeke speckle imaging on 24 June 2021, which showed
the same companion in the 0.83\,$\mu$m notch filter, but not the
$0.56\,\mu$m filter.  Figure~\ref{fig:kep1627binary} summarizes the
results of the high-resolution imaging.  Although the companion is
unresolved in the Gaia source catalog, its existence was also
suggested by the primary star's large RUWE, relative to other members
of the \cn.  The images yield a projected separation $\rho \approx
0\farcs16$, with $\Delta m_{832} \approx 3.1$ and $\Delta m_{\rm Kp} =
2.5$.  Using the measured Gaia EDR3 parallax for the system, this
implies a projected separation of $53 \pm 7$.  Given the low geometric
probably of a star imaged within $\rho \approx 0\farcs16$ to be a
chance companion along the line of sight, and the large observed RUWE,
we proceed under the assumption that the companion is bound, and that
the Kepler\,1627 system is binary.  Based on the
tabulation\footnote{\url{http://www.pas.rochester.edu/~emamajek/EEM_dwarf_UBVIJHK_colors_Teff.txt},
version \texttt{2021/03/02}.} by \citet{pecaut_mamajek_2013}, the
measured magnitude differences for a G8V primary correspond to a
spectral type for the companion of $\approx$M2V ($M_\star \approx
0.44\,M_\odot$).  However, the companion should have a longer
pre-main-sequence contraction phase than the primary, which would
imply that this mass is overestimated by $\sim10$ to $20\%$.

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Flares in Kepler\,1627}.  
    {\it Top:}
    The full short cadence Kepler dataset, acquired at 1-minute
    sampling (black points) is shown with a stellar variability model
    (blue line).
    {\it Middle:}
    Residual after subtracting the stellar variability model.  Flares
    appear as spikes.
    {\it Bottom:}
    Zooms of the brightest, and third-brightest flares.  A timing
    coincidence -- that both flares have ``successors'' approximately
    one orbital period after the initial event -- is emphasized.
		\label{fig:flarezoom}
	}
\end{figure*}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=1.0\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Phase-folded flares in Kepler\,1627}.  
    {\it Top:}
    As in the middle of Figure~\ref{fig:flarezoom}, phase-folded at
    the planet's ephemeris.
    {\it Bottom:}
    Fitted flare amplitudes and orbital phases -- each point
    represents one flare.
    Colors indicate relative time, from the beginning of the
    98-day short cadence Quarter 15 dataset (dark blue) to the end (light
    yellow).
    Lower amplitude flares likely exist in the data, and were not
    examined.
		\label{fig:flarephase}
	}
\end{figure*}

@@

In addition to the 3.9 years of long cadence data, short cadence
(1-minute) Kepler observations were acquired over 97.7 days during
Quarter 15.  The short cadence light curve shows a higher rate of
flaring than visible in the long cadence data
(Figure~\ref{fig:flarezoom}).  We analyzed the short cadence light
curve and its flares according to the following procedure.

For cleaning, we performed the following iterative detrending procedure.
\begin{enumerate}
  \item Model the starspot-induced variability using a
    Gaussian Process with a \texttt{SHOTerm} kernel (see
    Section~\ref{app:gptransit}), a white-noise jitter term, and the
    mean flux.  Fit the model to the time, flux, and flux uncertainty.
  \item Select points more than twice the median absolute
    deviation from the residual, and exclude them from the light
    curve (these points include the flares).  Repeat Step~1.
  \item Using the residual from Step 2, identify all flares,
    requiring them to be at least 20 cadences apart, at least 7 median
    absolute deviations above the median baseline, and lasting at
    least 2 cadences in duration.  Build the mask spanning these
    times, from 5 minutes before each flare begins to 2.5 minutes
    after the final flare cadence.  Repeat Step 1 a final time.
\end{enumerate}
The flares were identified and fitted using \texttt{altaipony}
\citep{davenport_2016,ilin_flares_2021}.  The analytic flare model is
from \citet{davenport_2014} and it parametrizes the flare with a start
time, an exponential lag time, and an amplitude.
Figure~\ref{fig:flarephase} shows the resulting flares, amplitudes,
and phases.

There were $N_{\rm f}=24$ flares that exceeded $0.5\%$ in relative
flux during the short cadence observations.  These 24 flares spanned a
total of 6.5 hours ($\sim$15 minutes per flare).  Whether it is
meaningful or not, we noticed a coincidence in the flare arrival
times.  The coincidence is that despite the low flare duty cycle, one
orbital period after the brightest flare, a second flare followed.
This and a similar event are shown in Figure~\ref{fig:flarezoom}.  The
timing error is good to a $\approx0.2\%$ difference from the orbital
period, which given the duty cycle seems {\it a priori} unlikely.  If
we consider flares falling within 2\% of the planet's orbital period
after a previous flare, then 4 of the 24 flare events have candidate
``successors''.
